Comparative Evaluation of Spark and Flink Stream Processing

### 2017-03-01 paper/paper.tex
updated  spark section

\section{Technical Background}
 In this section, we present the architecture, key characteristics, programming APIs  of Apache Spark, Apache Flink. The Apache Kafka platform is also discussed briefly.

@@

\par The main data abstraction in Spark is the Resilient Distributed Datasets (RDDs), which is a in-memory collection of elements partitioned across cluster of computers that can be processed in parallel \cite{rdd}. RDDs supports two categories of operations: transformations that drive new RDDs from the operated ones (e.g., map).  And actions which return a value (e.g., count).

//TODO: DStreams, streaming model

@@

\bibitem[5]{flink} 
Apache Flink. Available: https://flink.apache.org/ [Accessed February 2017].

\bibitem[6]{kafka} 
Apache Kafka. Available: https://kafka.apache.org/ [Accessed February 2017].

>>>>

\section{Technical Background}
 In this section, we present the architecture, key characteristics, programming APIs  of Apache Spark and Apache Flink. Moreover, a brief overview of the Apache Kafka platform is  provided.

@@

\par The main data abstraction in Spark core is the Resilient Distributed Datasets (RDDs), which is in-memory collection of elements partitioned across cluster of computers that can be processed in parallel \cite{rdd}. RDDs supports two categories of operations: transformations that drive new RDDs from the operated ones (e.g., map), and actions which return a certain value (e.g., count). On the other hand, the Discretized Stream (DStream) is the data abstraction in Spark Streaming, which is series of RDDs that represent an input stream of data \cite{spark_streaming}. In other words, the Spark Streaming is batch-based processing model, which process the continuous stream of data by divided into micro-batches to be processed by the Spark engine. Figure 1 illustrates the general process flow of Spark Streaming.

  \centering
    \includegraphics[width=.9\textwidth, height=.2\textheight]{streaming-flow.png}
     \caption{ Process flow of Spark Streaming \cite{spark_streaming}.}
\end{figure}

@@

\bibitem[5]{spark_streaming}
Spark Streaming. Available: http://spark.apache.org/docs/latest/streaming-programming-guide.html [Accessed March 2017].

\bibitem[6]{flink} 
Apache Flink. Available: https://flink.apache.org/ [Accessed February 2017].

\bibitem[7]{kafka} 
Apache Kafka. Available: https://kafka.apache.org/ [Accessed February 2017].
